---
title: "Amandafw_OriginalHomeworkCode_05"
author: "Amanda Wu"
date: "2023-11-12"
output: html_document
---

### [1] Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β
 coeffiecients (slope and intercept).
```{r Question 1}
library(curl)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall21/KamilarAndCooperData.csv") #loading data
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = TRUE) 
head(d) #making sure data is in 
model <- lm(data = d, log(HomeRange_km2) ~ log(Body_mass_female_mean)) #making the linear regression
model$coefficients #gives the slope and intercept 
summary(model)
```

### [2] Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each β coefficient.
  + Estimate the standard error for each of your β coefficients as the standard deviation of the sampling distribution from your bootstrap and determine the 95% CI for each of your β coefficients based on the appropriate quantiles from your sampling distribution.
  + How does the former compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?
  + How does the latter compare to the 95% CI estimated from your entire dataset?
```{r Question 2}
library(boot)
set.seed(1) 
bmodel <- function(d, inds) {
  data_samples <- d[inds, ] # generates samples from dataset 
  model <- lm(data = data_samples, log(HomeRange_km2) ~ log(Body_mass_female_mean)) # same model
  return(coef(model)) # prints
}

boot_results <- boot(d, bmodel, R = 1000) # boot function from documentation 
boot_results
sd(boot_results$t) # not positive if this is how you calculate SD ?
boot.ci(boot_results, conf = 0.95) # looks similar to the model ! 
```

```{r Question 2 CI and SE from D}
summary(model) 
confint(model)
```

The both the estimated 95% CI values and the SE values for the dataset and the bootstrapped sampling distribution are super close to each other. The bootstrapped sampling distribution seems to be a bit tighter but they are still really really close. 
